\cvsection{Education}

\cventry{\textbf{PhD Data Science} (forthcoming)}
{University of Earth} {Earth} {R, Julia, Turing.jl,
  Parallelization, spatial data} {Sept 2021 - March 2025}
\begin{itemize}
  \item Thesis: A mathematical model of internal migration (migrations
        on earth). For details see section ``Work Experience'' above.
        I hand in my thesis in February.
  \item Publication: Forthcoming, I hand in the paper in March.
\end{itemize}

\cventry{\textbf{Msc Statistics} (1.6)}{Earth University}
{Earth} {python, tensorflow} {Okt 2016 - July 2020}
\begin{itemize}
  \item Thesis: Deep Learning for Image Manipulation Detection (In
        cooperation with Earth GmbH) \\ I replicated a deep
        learning paper which applies the Faster R-CNN architecture to
        detect image manipulation. I successfully ran their model in
        \texttt{python} and \texttt{tensorflow}. This work included
        debugging their code, augmenting data, fine-tuning a
        pretrained network and exploring the architecture of CNNs.
\end{itemize}

% \cventry{\textbf{Bsc Mathematics} (-)}{University of Leipzig}
% {Leipzig} {-} {Okt 2015 - Okt 2016}
% \begin{itemize}
%   \item Completing successfully Calculus I, II and Linear Algebra I,
%         II as preparation for the MSc Statistics.
% \end{itemize}

\cventry{\textbf{BA Statistics} (1.6)}{University of Earth} {Earth}
{R, stan} {Okt 2012 - Sept 2016}
\begin{itemize}
  \item Thesis: An empirical evaluation of the randomized response technique. I developed a simple model in \texttt{R} and \texttt{stan} to analyze response rates to sensitive survey questions.
\end{itemize}
